New lower bounds for Schur and weak Schur numbers

### 2021-10-28 article/article.tex
verifs

\address[1]{CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190 Gif-sur-Yvette, France}
\address[2]{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France}

@@

\begin{keyword}
Schur number \sep Weak Schur number \sep Ramsey theory \sep Sumfree partition
\MSC[2020]{05D10 \sep 05A17 \sep 11B75 \sep 11B81}
\end{keyword}

>>>>

\address[1]{CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190, Gif-sur-Yvette, France}
\address[2]{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France}

@@

\begin{keyword}
Schur number \sep Weak Schur number \sep Ramsey theory \sep Sum-free partition
\MSC[2020]{05D10 \sep 05A17 \sep 11B75 \sep 11B81}
\end{keyword}
